Quotient maps and configuration spaces of hard disks

### 2022-02-09 manuscript/main.tex
code and data availability statement

\bmhead{Data availability} The data used to support the findings of this study are available from the corresponding author upon a reasonable request.

\bmhead{Code availability} The source codes used to generate the data of this study are available from the corresponding author upon a reasonable request.

>>>>

\bmhead{Data and code availability} The datasets and source codes associated with this study are available in the "quotient\_hard\_disks" repository, \url{https://github.com/burakericok/quotient_hard_disks}.
